%----------------------------------------------------------------------------------%
%   Sebastian Torrente's Master Curriculum Source Addendum I: Education			   %
%----------------------------------------------------------------------------------%
%
%	In this subcurriculum you can read with more detail about all the courses I've 
%   made, along with the things I've learnt in them. 	
% 
%----------------------------------------------------------------------------------%
%
%	Based on the template by Xavier Danaux (xdanaux@gmail.com) and using the 
%	moderncv package. Copyright 2006-2012
%
% 	This work may be distributed and/or modified under the
% 	conditions of the LaTeX Project Public License version 1.3c,
% 	available at http://www.latex-project.org/lppl/.
%
%----------------------------------------------------------------------------------%
%
%----------------------------------------------------------------------------------%
%   Index																	[Ind]  %
%----------------------------------------------------------------------------------%
%	This is a small index to jump to each part of the document.
%	
%	Index						-- [Ind]
%	Options						-- [Opt]
%	Theme						-- [The]
%	Personal Data				-- [Prd]
%	Content						-- [Con]
%		Education				-- [Edu]
%		Additional Education	-- [aEdu]
%
%----------------------------------------------------------------------------------%
%   Options 																[Opt]  %
%----------------------------------------------------------------------------------%
%   Fontsize: ('10pt', '11pt' and '12pt')
%   Papersize: ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper',
%		'landscape')
%   Type of font: ('sans' y 'roman')
\documentclass[11pt,a4paper,roman]{moderncv}

%----------------------------------------------------------------------------------%
%   Theme 																	[The]  %
%----------------------------------------------------------------------------------%

%	Options ('casual' (default),'classic', 'oldstyle', 'banking')
\moderncvstyle{casual} 

%	Colors ('blue' (default), 'orange', 'green', 'red', 'purple', 'grey' y 'black')
\moderncvcolor{black}

%	Fonts:
% \sdefault:  sans serif font
% \rmdefault: roman font
\renewcommand{\familydefault}{\rmdefault}
%\renewcommand{\familydefault}{\sdefault}

%	Number the pages?
\nopagenumbers{}                             

%	Codification:
%\usepackage[utf8]{inputenc}
%\usepackage{CJKutf8} 				%Just in case I need asian languages.

%	Margins:
\usepackage[scale=0.75]{geometry}			   % Margins. Recommended 0.75.
\setlength{\hintscolumnwidth}{2.3cm}           % Dates column's width

%----------------------------------------------------------------------------------%
%            Personal Data 													[Prd]  %
%----------------------------------------------------------------------------------%

\firstname{Sebasti\'an}
\familyname{Torrente Carrillo}

\title{Addendum I: Education}

%\address{Calle Jer\'onimo Santa Fe, 102, 2B}{30800 Lorca, (Murcia)}

%	Contact:

\mobile{(07423)~632~073}						%Spanish mobile phone                            
%\phone{+34~(968)~463~074}						%Placeholder for future british phone                            
%\fax{+34~(567)~890~123}						%Don't think I'll need it, but hey.

\email{sebastian.torrente@gmail.com}
%\homepage{infrafrequency.tumblr.com}
\homepage{es.linkedin.com/in/sebastiantorrentecarrillo/en}
\extrainfo{Skype: sebastiantorrente}

%	Photo:	
%\photo[64pt][0.4pt]{foto3} 		%[photoheight][framewidth]{nameofthephoto.jpg}

%Quotes
	%\quote{"Life is too short to be little"}
	%\quote{"Nobody is safe from the power of Science!"}

%----------------------------------------------------------------------------------%
%	Content 																[Con]  %
%----------------------------------------------------------------------------------%
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                     %For CV in Chinese
\maketitle


%----------------------------------------------------------------------------------%
%	Profile																	[Pro]  %
%----------------------------------------------------------------------------------%

%\section{Profile}
%\cvitem{}{
%With a population of almost 460,000, Manchester is the UK's third largest city yet widely regarded as Britain 's second city and arguably the most exciting, cultural and forward-thinking. The decline of manufacturing and heavy industry in the 1980s and the subsequent dramatic rise in unemployment, provided a powerful catalyst for the city to regenerate itself and seek a new direction. And the main engine for this came in the wake of the IRA bomb attack in 1996.
%}

%----------------------------------------------------------------------------------%
%	Education 																[Edu]  %
%----------------------------------------------------------------------------------%
\section{Education}

\cventry{2001-2013}
	{Licentiate Degree in Physics}
	{University of Murcia}
	{Murcia}
	{}
	{Equivalent to a BS+MS. Specialization in \textit{'Electronics and automatics.'}
	 With also computational physics and astrophysics classes due to personal interest.
	\begin{itemize}
		\item A Grades: Nuclear and Particle Physics, General Relativity and 
		Cosmology, Groups Theory Applied to Physics.
		\item B Grades:	Computational Physics, Advanced Simulations, Robotics, 
		Photonics.
		\item Student intern in the class 'General Relativity and Cosmology'.
%		\item Recovered from the big mistakes and personal problems I've had during 
%		my first years in college.
		\item Volunteered to edit and typeset the compilation book with all the 
		papers wrote for the Nuclear Physics class, which will be published. I got 
		more experience with \LaTeX, rewriting and turning the 
		papers into a single book with an unified style.
		\item Staff member in the \textit{\href{http://www.um.es/fispac/}
		{FISPAC}} stand during \textit{\href{http://www.f-
		seneca.org/secyt10/home.php}{SECyT 2010}}. Contributed with the creation of 
		posters and flyers and also giving divulgation speeches about astro and 
		particle physics to a wide variety of public. Solved the shortage of material 
		by creating a mailing list. Everyone interested was welcome to register so we 
		could send them digital versions of the posters. Thanks to this, FISPAC got 
		in contact with a lot of high schools for future divulgation activities.
	\end{itemize}	
	}

%----------------------------------------------------------------------------------%
%	Additional Education													[aEdu] %
%----------------------------------------------------------------------------------%

\section{Additional education}

% Sample Entry:
%\cventry{year--year}
	%{Degree}
	%{Institution}
	%{City}
	%{\textit{Grade}}
	%{Description}

\cventry{2012}{\href{https://6002x.mitx.mit.edu/}
	{6.002x Circuits and Electronics}}
	{MITx}
	{}
	{}
	{Took this course to refresh my knowledge in electronics and to test online 
	education. 
	Verification code: \newline{} \url{https://verify.edxonline.org/cert/e9af31ea9ce7435fa021ca908b4bfeac}}

\cventry{2012}
	{\href{https://www.edx.org/courses/BerkeleyX/CS169.1x/2013_Spring/about}
	{CS169.1x and 2x: Software as a Service}}
	{Edx}
	{}
	{}
	{It was a good way to learn Agile Development techniques and also give a try to 
	Ruby and Rails. After this course I added Git into my arsenal of tools. \\ 
	Verification codes: \\ \url{https://verify.edx.org/cert/61e969054b3e4edeacb84805c41d4301} and \\ \url{https://verify.edx.org/cert/29cf1609f4c540c38f0eea4184ff9670}}

\cventry{2012}
	{\href{https://6002x.mitx.mit.edu/}
	{CS188.1x: Artificial Intelligence}}
	{Edx}
	{}
	{}
	{Took this course out of curiosity and because it requires some Python 
	programming I could use as training.\\
	Verification codes: \\ 	\url{https://verify.edx.org/cert/2907f427165e4e3d85036db258752aab}}


\cventry{2010}
	{Astroparticles: what is the universe made of?}
	{University of Alcal\'a}
	{Siguenza}
	{}
	{Summer Course, 25 hours. Due to my good relations with the teacher Javier 
	Bussons Gordo I went to a course organiseb by him. Got into contact with a lot of 
	interesting projects like the particles observatory in Canfranc and the 
	Consolider Multidark.}

\cventry{2008}
	{\href{http://biplot.usal.es/verano/analisis-estadistico-de-dat.html}
	{Statistical Analysis of Data with SPSS}}
	{University of Salamanca}
	{Salamanca}
	{}
	{Summer Course, 30 hours. I wanted to visit Salamanca and learn a little bit of 
	SPSS to see if it was a tool I could use in the future.}

\cventry{2008}{\href{http://mat.uab.cat/~oalgebras/}
	{Schools of Mathematics Lluis Santal\'o. Aspect of operator algebras and 
	applications}}
	{International University Men\'endez Pelayo}
	{Santander}
	{}
	{30 hours summer course. My goals were to meet people, learn some state of the 
	art math and practice my english.}

\cventry{2007}
	{\href{http://cursosdeverano.unican.es/cursos-anteriores/Paginas/Detalle-
	curso.aspx?p_id=1094}
	{Artificial Vision}}
	{University of Cantabria}
	{Santander}
	{}
	{Summer Course, 20 hours.}

\cventry{2007}
	{Quantum computation and topological orders}
	{Complutense University of Madrid}
	{San Lorenzo del Escorial}
	{}
	{Summer Course, 30 hours. As a course in english, it was a great opportunity to 
	practice with the language and talk with physicist from all over the world.}

\cventry{2006}
	{Hidrogen and fuel batteries: energy for the XXI century}
	{UNED}
	{El Barco de avila}
	{}
	{Summer Course, 18 hours.}

\cventry{2006}					{\href{http://portal.uned.es/portal/page?_pageid=93,22547880&_dad=portal&_schema=PORTAL&idCurso=042}		{Process Control: Applications in MATLAB-SIMULINK}}
	{UNED}
	{\'Avila}
	{}
	{Summer Course, 35 hours. I wanted to try summer courses as a way of having more 
	productive summer holydays and to learn uses of MATLAB other than the ones I did 
	in college.}

\cventry{1992-2001}
	{Bachelor of Music}
	{Conservatory of Lorca}
	{Lorca}
	{}
	{Violin.}

%----------------------------------------------------------------------------------%
%	Master Thesis																   %
%----------------------------------------------------------------------------------%

%\section{Master Thesis}
	%\cvitem{titulo}{\emph{Title}}
	%\cvitem{sinodares}{Sinodares}
	%\cvitem{descripcion}{Brief Descrition}


\end{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%